% !TEX program = pdflatex

\documentclass{article}

\usepackage{geometry}
\usepackage{multirow}
\usepackage{hyperref}

\hypersetup{%
pdftitle = {Macmillan Education Student Application User Feedback Report},
pdfauthor = {Potsawat Thinkanwatthana},
pdfkeywords = {{macmillan}, {education}, {app}}}

\geometry{%
a4paper}

\title{Macmillan Education Student Application\\
User Feedback Report}
\author{Potsawat Thinkanwatthana\\
Department of Computer Science, Faculty of Science\\
Kasetsart University, Bangkok, Thailand\\
potsawattkw@outlook.com}
\date{\today}

\begin{document}
\begin{titlepage}
\maketitle
\thispagestyle{empty}
\tableofcontents
\end{titlepage}

\section{Introduction}
My name is Potsawat Thinkanwatthana, a Macmillan Education Student app user. I have been using the Macmillan Education Student app
both the web client and the mobile client versions. At the moment, I have faced some issues using the app
and wish to report them to the developers. Those issues involve:
\begin{itemize}
\setlength\itemsep{0ex}
    \item Class management system
    \item Session authentication and management system
    \item Offline material management
    \item Working progress monitoring
    \item User interface: page transitioning, screen rotation
    \item Note taking feature
\end{itemize}
I will explain the details about each of the issues and steps to reproduce some of them later in section \ref{sec:detailed-explanation} on page \pageref{sec:detailed-explanation}.
If there is any other required information, you can ask me by writing to potsawattkw@outlook.com.

\section{Environment}
There are two client versions of the app I have been using---the web and mobile client.

\subsection{Web Client}
\begin{tabular}{p{7em} l}
Environment     & PROD\\
Version         & 1.6.1.76\\
Browser         & Google Chrome Desktop (Stable Release)\\
Browser Version & 103.0.5060.134 (Official Build) (arm64)
\end{tabular}

\subsection{Mobile Client}
\begin{tabular}{p{7em} l}
Environment     & PROD\\
Version         & 1.5.7.74\\
Device          & Apple iPad Pro (10.5-inch)\\
OS              & iPadOS\\
OS Version      & 15.6 (19G71)
\end{tabular}

\pagebreak[4]

\section{Detailed Explanation}
\label{sec:detailed-explanation}
Issues I have faced:
\begin{enumerate}
\setlength\itemsep{0ex}
    \item There is no option to leave the joined classes. Students should be able to leave a class that they are no longer attended by themselves.
    \item The login page always shows up even already logged in to a session.
    \item On the mobile client version, the offline material management is unstable.
    \item While working on an activity, if the page was reloaded, the current working progress will be reset and recounts only new activities that were not touched.
            Thus, reattempting recently attempted activity is not possible until the last one in the assignment is reached.
    \item Note taking feature is buggy and sometime does not load some saved notes.
    \item Pages take too long to load, including those have been downloaded to the device.
    \item On iPadOS mobile clients, the main menu view cannot goes landscape.
\end{enumerate}

\subsection{Class Management}
My teacher and I have came across problems with the app's class management system as it is not
possible for students to leave classes.

\subsubsection*{Steps to Reproduce}
Supposed that a student wants to join a class, $A$, but entered a wrong class code which refers to another class, $B$.
\begin{center}
\fbox{\begin{minipage}[c]{\textwidth}
\begin{enumerate}
    \item Enters $B$ class code into the app to join the class.
    \item Enters $A$ class code into the app to join the class.
    \item Now, there are 2 classes have been joined so far but there is no way to leave any of them.
\end{enumerate}
\end{minipage}}
\end{center}

\subsection{The Login Page}
Everytime I open the app on my tablet, I got the login page regardless of my current login status.
\end{document}
